---
title: "Final Presentation"
author: "Zoe Robino"
date: "`r format(Sys.time(), '%B %d, %Y @ %I:%M %p')`"
output: ioslides_presentation
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

## Packages Used

I used tidyverse for data manipulation and plotting.

```{r, echo = TRUE}
library(tidyverse)
```




I need scales to format a percentage axis.

```{r, echo = TRUE}
library(scales)
```






## Harry Potter Movies Dataset: Characters 

I compiled my dataset by using the web site Kaggle [Harry Potter Movies Dataset](https://www.kaggle.com/datasets/maricinnamon/harry-potter-movies-dataset?resource=download). Then took the subset dataset for characters

The dataset was last updated 4 months ago, so some of the values may have changed between then and now. 

**Variables in the Dataset:**

* `'Character ID'`: Assigned id number for each character 
* `'Character Name'`: Character names from all Harry Potter movies 
* `Species`: Characters creature type in Harry Potter movie(Human,Ghost,Centaur, Half-Human/Half-Giant, Werewolf, etc)
* `Gender`: The gender for each character (Female/Male)

## 

* `House`: The sorted house for each charcter(Gryffindor, Slytherin, Ravenclaw, Hufflepuff,Beauxbatons Academy of Magic and Durmstrang Institute)
* `Patronus`: The patronus spirt gardiun for each character(Stag, Doe, Cat, Jack Russell Terrier,Otter, ect)
* `'Wand (Wood)`: wood type for each characters wand(Yew,Cherry,Holly,Vine and Elder)
* `'Wand (Core)`: core type of each charcters wand(Dragon Heartstring,Unicorn Hair,Phoenix Feather,Thestral Tail Hair, etc))

##

```{r}
Characters <- read_csv("data/Characters.csv")
glimpse(Characters)
```

##

```{r, fig.align = "center", fig.width = 7.5}
library(treemap)
 house <- c(Characters$House)
names <- c(Characters$`Character ID`)
subgroup<-frequency(data)
 data <- data.frame(house,names)
 
 treemap(data,
             index="house",
             vSize="names",
             type="index",
             title="Houses")
            
```



##

```{r, fig.align = "center", fig.width = 7.5}

my_table1 <- table(Characters$Species)
ggplot(data=subset(Characters, !is.na(House)), aes(x = frequency(Species), y = Species,fill = House)) +
  geom_col()+
  facet_grid(.~House)+
  labs(x = "Frequency", y = "Species", title = "Frequency of Species in each House") + 
  theme(plot.title = element_text(hjust = 0.5))

```


##

THANK YOU!



